# Survey on Bayesian Networks\n\n## Abstract\n\nBayesian networks are a tool that allows for modeling and probabilistic reasoning about complex problems. They are based on the concept of conditional independence and allow for a compact representation of joint probability distributions. The field of Bayesian networks has been developed for more than 30 years and has become a widely used tool in the field of artificial intelligence.\n\n## Introduction\n\nBayesian networks are a tool for modeling and probabilistic reasoning about complex problems. They are based on the concept of conditional independence and allow for a compact representation of joint probability distributions. The field of Bayesian networks has been developed for more than 30 years and has become a widely used tool in the field of artificial intelligence.\n\n## Bayesian Networks\n\nA Bayesian network is a graphical representation of a joint probability distribution. A joint probability distribution is a distribution over a set of random variables \\(X=\\{X_{1},\\dots ,X_{n}\\}\\). It is represented as\n\n\\[P(X_{1},\\dots ,X_{n})=P(X)\\]\n\nand is a function that maps each possible combination of values of \\(X\\) to a probability. A Bayesian network represents this joint probability distribution in a compact way.\n\nThe structure of a Bayesian network is a directed acyclic graph (DAG) that consists of a set of nodes \\(X\\) and a set of directed edges \\(E\\). Each node \\(X_{i}\\) represents a random variable. Each edge \\((X_{i},X_{j})\\) represents a conditional dependence of the random variable \\(X_{i}\\) on the random variable \\(X_{j}\\). If there is an edge \\((X_{i},X_{j})\\), then \\(X_{i}\\) is a parent of \\(X_{j}\\) and \\(X_{j}\\) is a child of \\(X_{i}\\).\n\nEach node is associated with a conditional probability distribution that quantifies the strength of the conditional dependence between a node and its parents. The joint probability distribution can be computed by multiplying the conditional probability distributions of all nodes.\n\nThe Bayesian network is a compact representation of the joint probability distribution. The size of the joint probability distribution is exponential in the number of random variables \\(X\\). In contrast, the size of the Bayesian network is linear in the number of random variables \\(X\\).\n\n## Bayesian Network Learning\n\n### Bayesian Network Structure Learning\n\nThe structure of a Bayesian network is a directed acyclic graph (DAG). This means that there are no cycles in the graph. Finding a Bayesian network structure is an NP-hard problem. This means that there is no known efficient algorithm for finding an optimal Bayesian network structure. The most common algorithms for learning the structure of a Bayesian network are based on two approaches: constraint-based and score-based.\n\n#### Constraint-based Algorithms\n\nConstraint-based algorithms are based on the concept of conditional independence. These algorithms use conditional independence tests to find a Bayesian network structure that represents the conditional independences in the data. The most common conditional independence test is the mutual information test.\n\n#### Score-based Algorithms\n\nScore-based algorithms are based on a scoring function. The scoring function is a measure of how well a Bayesian network structure fits the data. A common scoring function is the Bayesian information criterion (BIC).\n\n### Bayesian Network Parameter Learning\n\nThe parameters of a Bayesian network are the conditional probability distributions of all nodes. The parameters of a Bayesian network can be learned from data. There are several different approaches for learning the parameters of a Bayesian network: maximum likelihood estimation, Bayesian estimation and Bayesian updating.\n\n## Applications\n\nBayesian networks are used in many different fields, including artificial intelligence, natural language processing, data mining, computer vision, bioinformatics, robotics and control theory.\n\n### Artificial Intelligence\n\nBayesian networks are a common tool for knowledge representation and probabilistic reasoning in the field of artificial intelligence. Bayesian networks are used in robotics, computer vision, expert systems and natural language processing.\n\n### Data Mining\n\nData mining is the process of discovering patterns in large datasets. Bayesian networks are a tool that can be used for classification and prediction. They are especially useful in the case of missing data.\n\n### Bioinformatics\n\nBioinformatics is the field of research that applies computational techniques to biological data. Bayesian networks are used for many different tasks in bioinformatics, including modeling biological systems, learning from biological data and prediction of biological data.\n\n## Software\n